%\title{Example letter using the newlfm LaTeX package}
%
% See http://texblog.org/2013/11/11/latexs-alternative-letter-class-newlfm/
% and http://www.ctan.org/tex-archive/macros/latex/contrib/newlfm
% for more information.
%
\documentclass[12pt,stdletter,orderfromtodate,sigleft]{newlfm}
\usepackage{blindtext, xfrac}
 
\newlfmP{dateskipbefore=40pt}
\newlfmP{sigsize=40pt}
\newlfmP{sigskipbefore=40pt}
 
\newlfmP{Headlinewd=0pt,Footlinewd=0pt}
 
\namefrom{Braden Beck}
 
\addrto{%
County of San Luis Obispo \\
Assessor's Office
}
 
\dateset{July 26, 2019}
 
\greetto{Application for the position of Software Engineer,}
 
\closeline{Thanks,}
 
\begin{document}
\begin{newlfm}
As a victim of this county's poor documentation practices I feel it is my civic duty to apply for this position. Earlier this year your payment processor messed up a property tax payment of mine and I dove into what exactly went wrong only to find out that the issues where so systemic to how your office operates that attempting to change them would cost me a lot of valuable time. I see this as an opportunity to fix all the grievances I have with the way you all do business and make this county a place where I am proud rather than ashamed to live in. Working for Amazon I have skills in dealing with problems at a much larger scale than SLO county and I believe my expertise would be invaluable in your efforts to reshape the tree killing bureaucratic nightmare that is the county office into a lean paperfree automated system that eats taxes for breakfast. I have designed and built many web applications, including those that deal with maps and geographical data, I have experience with database and data sets larger than any available in SLO county. And best of all I know how to do it all using free (as in freedom) and open source software so you don't have to pay Microsoft to hold your hand. You (the county) should be the owner of all your software solutions making the only cost to you the electricity for computers (which would be even cheaper if diablo wasn't to be shut down (sorry for the politics but you are a government office and I'd be remiss not to hold you accountable)). Listen in all seriousness I think I'm overqualified for this position and where I to accept your max salary of engineer III is less than half of what I make now. However I'm not money driven, I want to give back to this community and I want to help eliminate all the dumb stuff (technology wise) your office does on a daily basis that hurts citizens like me and grandma Jane who's been in payment grace period for her property taxes for months cause she just can't figure out how to make a payment on your broken website. My motto, work smarter not harder, and I hope to help your office embody that.  My contact info and credentials are in my resume please reach out if you have any questions!
\end{newlfm}
\end{document}

