%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Braden Beck}
\address{(+1)808-635-3399 \\ bradabraden@gmail.com \\ github.com/bbeck13}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf California Polytechnic State University} \hfill {\em Sep 2013 - Jun 2017} 
\\ Bachelor of Science
\\ Computer Science - College of Engineering 
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Lisp, Racket, Java, JavaScript, C/C++, Python  \\

Software \& Tools & LaTeX, bash, vim, React, RDS/SQL, AWS, JTS/JSTS, GNU + Linux \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Amazon Prime}{\em August 2017 - August 2018}{Software Development Engineer}{}
\item Migrated accounting reconciliation data off of oracle to postgres rds while maintaining SOX compliance.
\item Managed data for Prime Plans, maintained and developed website with tooling around Prime Plans including visualizing free trial and renewal logic.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Amazon Last Mile Technology}{\em August 2018 - November 2019}{Software Development Engineer 2 (L5)}{}
\item Created system to algorithmically simplify and propagate GIS data to downstream systems to affect package labeling and ultimately drive roll-out of a new routing model for all Amazon Delivery Stations in the United States and Europe.
\item Worked on full stack React based web app that allows users to define/configure geographic areas for Delivery Stations.
\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{AWS Security}{\em November 2019 - Feb 2021}{Software Development Engineer 2 (L5)}{}
\item Built ETL system for processing and delivering security agent logs and much more, dealing with petabytes of security data.
\item Used state of the art infrastructure as code on AWS to create and manage entire cloud infrastructure systems through code.
\item Integrated with crowdstrike and splunk to gather, organize and monitor security logs.
\end{rSubsection}
\end{rSection}

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements} \itemsep -2pt
\item Deans List for 4 quarters (when I took only CS classes)
\item TA for 2 years. Taught a lot of students about systems programming, I believe anyone can learn CS if they just apply themselves.
\end{rSection}

\begin{rSection}{Projects} \itemsep -2pt
\begin{rSubsection}{RhythmRunner}{github.com/bbeck13/RhythmRunner}{c++/opengl}{}
\item Organized and manged small group project to create a cross platform video game using opengl. Created level editor / procedural generated levels based on audio signals so that players movement was in time with music

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular}
\begin{rSubsection} {Outrigger Canoeing}{June 1994 - Present}{}{}
\item \href{https://www.patagonia.com/blog/2018/02/a-thirty-five-year-voyage-back-in-time/}{https://www.patagonia.com/blog/2018/02/a-thirty-five-year-voyage-back-in-time/}
\item \href{https://hanahou.com/22.2/outrigger-odyssey}{https://hanahou.com/22.2/outrigger-odyssey}
\end{rSubsection}
\end{rSection}
\end{document}
